How much variance in AUC-ROC is there between model runs?

### 2020-06-09 rep_nosmooth/variance.Rmd
add Goldstein to variance note
generally still the case that varation is within 0.01, with some outliers for Quad

model_table <- crossing(
  model   = c("Escalation", "Quad"),
  horizon = c("1 month", "6 months"),
  sample  = c(1:SAMPLES)
)

@@

```{r}
# I want to add horizontal lines at the boundaries for rounding AUC-ROC to 
# two digits. Since the plot below is faceted, need to use a separate data frame
# for this with facet variable
hlines <- bind_rows(
  tibble(smoothed = "Smoothed", horizon = "1 month", 
         y = c(.79, .80, .81, .82, .83, .84, .85) + .005),
  tibble(smoothed = "Original", horizon = "1 month", 
         y = c(.77, .78, .79, .8) + .005),
  tibble(smoothed = "Smoothed", horizon = "6 months", 
         y = c(.77, .78, .79, .80, .81, .82) + .005),
  tibble(smoothed = "Original", horizon = "6 months", 
         y = c(.76, .77, .78, .79) + .005)
)

>>>>

model_table <- crossing(
  model   = c("Escalation", "Quad", "Goldstein"),
  horizon = c("1 month", "6 months"),
  sample  = c(1:SAMPLES)
)

@@

```{r}
# I want to add horizontal lines at the boundaries for rounding AUC-ROC to 
# two digits. Since the plot below is faceted, need to use a separate data frame
# for this with facet variable
hlines <- bind_rows(
  tibble(horizon = "1 month", smoothed = "Original", 
         y = c(.77, .78, .79, .8, .81) + .005),
  tibble(horizon = "1 month", smoothed = "Smoothed", 
         y = c(.78, .79, .80, .81, .82, .83, .84, .85) + .005),
  tibble(horizon = "6 months", smoothed = "Original", 
         y = seq(.76, .83, by = 0.01) + .005),
  tibble(horizon = "6 months", smoothed = "Smoothed", 
         y = seq(.76, .82, by = 0.01) + .005)
)
